Ultra-deep $K_s$-band Imaging of the \textit{Hubble} Frontier Fields

### 2015-02-21 Paper0/ms.tex

>>>>

\end{document}
=======
\documentclass[iop, numberedappendix]{emulateapj}
\usepackage{apjfonts}
%\documentclass[12pt,preprint]{aastex}

K-band surveys:  ISAAC, NMBS, UltraVISTA, ...

HUGS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                %
%  Summary table
%                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{lrcclrrcc} 
\tabletypesize{\footnotesize}
\tablewidth{0pt} 
\tablecaption{Field summary \label{tab:summary}} 
\tablehead{ 
\colhead{Field} & \colhead{$z$} & \colhead{R.A.} & \colhead{Dec.} & \colhead{Instrument} & \colhead{Epoch} & \colhead{$t$} & \colhead{Depth} & \colhead{FWHM}}
\startdata 
Abell 2744 & 0.308 & 00:14:21.2 & -30:23:50 & \textit{VLT}/HAWKI     & 2013 Oct 24--2013 Dec 24 & 29.4 h & 25.8 & $0\farcs40$ \\ 
MACS-0416  & 0.396 & 04:16:08.9 & -24:04:28 & \textit{VLT}/HAWKI     & 2013 Oct 25--2014 Feb 23 & 25.5 h & 25.9 & $0\farcs38$ \\ 
MACS-0717  & 0.545 & 07:17:34.0 & +37:44:49 & \textit{Keck}/MOSFIRE  & 2015 Jan 26--27                 & \xxx & 25.0 & $0\farcs43$ \\ 
MACS-1149  & 0.543 & 11:49:36.3 & +22:23:58 & \textit{Keck}/MOSFIRE  & 2015 Feb 24                    & \xxx & \xxx & \xxx
\enddata 
%\vspace{-0.8cm} 
\tablecomments{Depth is defined as the 5$\sigma$ limiting magnitude for point sources, measured in $D=0\farcs5$ apertures (\S\ref{s:depth}).} 
\end{deluxetable*}
%\vspace{1cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\plotone{hawkiff_layout.pdf} % Figures/exposure_map.pdf
\caption{Layout of the Frontier Fields $K_s$-band mosaics.  The positions of the \textit{HST} cluster and parallel fields are shown in the blue (ACS optical) and red (WFC3 IR) polygons.  The area covered by the \textit{Spitzer}/IRAC 3.6 and 4.5\,\mum\ channels is shown in orange.  The bottom panels show the exposure maps, where the four HAWK-I chips and two MOSFIRE pointings can be seen.\label{fig:layout}}  
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The product of the inverse curves of growth shown in Fig.~\ref{fig:cog} (i.e., aperture corrections) and the noise curves in the top panel of Fig.~\ref{fig:depth} defines an optimal photometric aperture size where this product is minimized \citep{whitaker:nmbs}.  For our $K_s$-band mosaics, this optimal aperture has $D\sim0\farcs5$, just larger than the FWHM of point-source profiles.  The $5\,\sigma$ limiting magnitudes (AB) within $0\farcs5$ diameter apertures are 25.8, 25.9, and 25.0 in the Abell 2744, MACS-0416, and MACS-0717 fields, respectively.  We note that the depths of the FF HAWK-I mosaics are nearly identical to those of the two deepest HUGS pointings in the GOODS-South Field (i.e., GOODS-South ``D1'' and ``D2'').  The image depths reported by \cite{hugs} assume ideal noise properties that can be compared to the dashed curves in Fig.~\ref{fig:depth}.  We have analyzed the HUGS GOODS-South ``D2'' image with the same empty-aperture technique as was done for the FF images, and the sensitivities are fully consistent with those reported by \cite{hugs} when accounting for the different definitions.  Along with the two HUGS deep HAWK-I fields, our images covering the Frontier Fields represent the deepest $K_s$-band images ever obtained and will provide a crucial complement to the deep \textit{HST} and \textit{Spitzer} imaging of the same fields.
